\section{Faults Discovered Using TSTL}
\label{sec:bugs}

\subsection{ArcPy Faults}

\begin{figure}
{\scriptsize 
\begin{code}
shapefilelist0 = glob.glob("C:\\Arctmp\\*.shp")                             \textcolor{black!60}{\# STEP 0}
\textcolor{black!60}{\#[}
shapefile0 = shapefilelist0 [0]                                           \textcolor{black!60}{\# STEP 1}
newlayer0 = "l1"                                                          \textcolor{black!60}{\# STEP 2}
\textcolor{black!60}{\#  or newlayer0 = "l2" }
\textcolor{black!60}{\#  or newlayer0 = "l3" }
\textcolor{black!60}{\#  swaps with steps 3 4 5 6 7}
\textcolor{black!60}{\#] (steps in [] can be in any order)}
\textcolor{black!60}{\#[}
featureclass0 = shapefile0                                                \textcolor{black!60}{\# STEP 3}
\textcolor{black!60}{\#  swaps with step 2}
fieldname0 = "newf1"                                                      \textcolor{black!60}{\# STEP 4}
\textcolor{black!60}{\#  or fieldname0 = "newf2" }
\textcolor{black!60}{\#  or fieldname0 = "newf3" }
\textcolor{black!60}{\#  swaps with steps 2 8}
selectiontype0 = "SWITCH\_SELECTION"                                       \textcolor{black!60}{\# STEP 5}
\textcolor{black!60}{\#  or selectiontype0 = "NEW\_SELECTION" }
\textcolor{black!60}{\#  or selectiontype0 = "ADD\_TO\_SELECTION" }
\textcolor{black!60}{\#  or selectiontype0 = "REMOVE\_FROM\_SELECTION"}
\textcolor{black!60}{\#  or selectiontype0 = "SUBSET\_SELECTION"}
\textcolor{black!60}{\#  or selectiontype0 = "CLEAR\_SELECTION"   }
\textcolor{black!60}{\#  swaps with steps 2 8}
op0 = ">"                                                                 \textcolor{black!60}{\# STEP 6}
\textcolor{black!60}{\#  or op0 = "<" }
\textcolor{black!60}{\#  swaps with steps 2 8}
val0 = "100"                                                              \textcolor{black!60}{\# STEP 7}
\textcolor{black!60}{\#  or val0 = "1000" }
\textcolor{black!60}{\#  swaps with steps 2 8}
\textcolor{black!60}{\#] (steps in [] can be in any order)}
arcpy.MakeFeatureLayer\_management(featureclass0, newlayer0)               \textcolor{black!60}{\# STEP 8}
\textcolor{black!60}{\#  swaps with steps 4 5 6 7}
arcpy.SelectLayerByAttribute\_management(newlayer0,selectiontype0,
   ' "'+fieldname0+'" '+op0+val0)                                         \textcolor{black!60}{\# STEP 9}
arcpy.Delete\_management(featureclass0)                                    \textcolor{black!60}{\# STEP 10}
arcpy.SelectLayerByAttribute\_management(newlayer0,selectiontype0,
   ' "'+ fieldname0+'" '+op0+val0)                                        \textcolor{black!60}{\# STEP 11}
\end{code}
}
\caption{Deleting a feature class does not invalidate or delete layers that depend on it.}
\label{fault1}
\end{figure}

In the process of testing ArcPy with TSTL, we discovered at least five
distinct faults
(thus far) that can cause an ArcPy script to crash.  While we have (as
discussed in Section \ref{sec:lang}) some properties that check for
data corruption and determinism of GIS analysis, we are not focusing
on these until we have a reliable way to avoid system crashes.   In
order to give an idea of what TSTL test cases look like, we discuss
briefly one of these ArcPy crashes.

ArcPy crashes when the feature class from which a layer is produced is
deleted, and the layer is used in a {\tt SelectLayer} call (this
version shows an attribute-based selection, but location selection
will cause the same problem): (Figure \ref{fault1}).  The underlying issue seems to be that
while operations on a deleted feature class properly notify a user the
feature class does not exist, ArcPy or ArcGIS does not track that
layers produced from a feature class should also be deleted/invalidated
when the feature class is deleted.  Layers are not copies
of a feature class, but essentially new \emph{views} of a feature class.
This means that when the underlying feature class is modified or
deleted, the view needs to be updated to reflect that change, and this
is not correctly implemented.  Figure \ref{fault1} shows part of an
annotated, reduced, normalized, and generalized test stand-alone test
case (with the boilerplate, function definitions, and imports
removed) for this fault.  The final line of code crashes ArcPy and the
Python interpreter.  Comments indicate alternative similar tests that
also fail.  In this case, TSTL's additional reduction steps (based on
term rewriting in the action language) remove almost half the steps in
the original, delta-debugged test case.

Other faults (or documentation lapses) in ArcPy we have discovered include crashes when computing
statistics over database fields of a layer using a deleted field and
crashes due to seemingly reasonable modifications of feature classes
while a database cursor is active.  In order to deal with the latter,
which seems more in the line of an undocumented behavioral restriction
than a ``bug,'' we now drastically limit database modification when a
cursor is active.  We have reported these problems to Esri, but have
not received a response.  The problems discovered may be previously
known to Esri, but are not generally known to the ArcPy user
community, and those that could be considered API limitations (that
cause unexplained crashes when violated) are not documented.

\subsection{Faults in Other Systems}

TSTL  is only slightly less than two years old, and a stable, mature,
non-prototype version has only existed for about a year.   However,
TSTL has already been used to find important bugs in real systems.

Using TSTL's support for differential testing, we were able to 
quickly find 
and report issues with the widely-used {\tt gmpy2} interface to the GMP (GNU 
Multiple Precision \cite{gmp} arithmetic library), as well as 
(surprisingly) in the core CPython bignum implementation
\cite{gmpy2bugs,cpythonbug}. 


TSTL was also able to discover at least 15
previously undiscovered faults in the widely used SymPy library for
symbolic mathematics in Python \cite{sympy}.  We have reported these
faults, and hope to collaborate with the SymPy team to provide
assistance in localizing and fixing them using TSTL.  The SymPy
effort was able to move from
decision-to-test to first discovered fault in the course of a single
day, due to the much higher ease-of-use for the post-ArcPy version of
TSTL used.  For a straightforward testing task like SymPy, building a
TSTL harness is now quite simple, largely a matter of thinking about
what the user wishes to test.

Students using TSTL in graduate classes on software testing have
already, with minimal assistance, discovered faults in some real-world
systems.  Not all of these are confirmed and reported yet.  TSTL
testing revealed a fault in either the widely-used {\tt PyOpenCL}
library \cite{PyOpenCL}, the even more widely-used {\tt OpenCL}
infrastructure \cite{OpenCL}, or (possibly) the NVIDIA hardware being
used.  We are still investigating this problem, but it appears to be a
genuine fault, though debugging and assigning blame is complex due to
the layers of software and hardware involved.  Second, TSTL testing
found cases where distance metrics that were supposed to be symmetric
in the popular fuzzy-string-matching library FuzzyWuzzy
\cite{FuzzyWuzzy} were asymmetric, if the default Python string match
library was used instead of a Levenshtein-distance library.  Third,
TSTL testing revealed numerous problems with the {\tt astropy.table}
module of the AstroPy library \cite{AstroPy}, used by many
professional astronomers and astrophysicists.  TSTL has also been used
to discover faults in the TSTL API itself.  The github repository for
the graduate class in question
(\url{https://github.com/agroce/cs562w16}) contains the TSTL code for
testing these systems (and many other student projects).
