%\documentclass{sig-alternate}
\documentclass[sigconf]{acmart}
\usepackage{graphicx}
\usepackage{pifont}
\usepackage{url}
\usepackage{code}
\usepackage{amsmath}
\usepackage{algpseudocode} 
\usepackage{algorithmicx}
\usepackage{algorithm}
\usepackage{xcolor}
\usepackage{balance}
%\usepackage{flushend}

\newcommand{\mycomment}[1]{}

\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
%\acmDOI{10.475/123_4}

% ISBN
%\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[ISSTA'17]{International Symposium on Software Testing
  and Analysis}{July 2017}{Santa Barbara, California, USA}
\acmYear{2017}
\copyrightyear{2017}


\begin{document}

\title{One Test to Rule Them All}
%\title{Normalizing and Generalizing Test Cases}

\author{Alex Groce}
\affiliation{
\institution{School of Informatics, Computing, and Cyber Systems, 
  Northern Arizona University, USA}}
\email{agroce@gmail.com}

\author{Josie Holmes}
\affiliation{Pennsylvania State University, USA}
\email{}

\author{Kevin Kellar}
\affiliation{Crescent Valley High School, Corvallis, Oregon, USA}
\email{}

%\numberofauthors{3}

\author{}

\author{}
%\alignauthor
%Alex Groce\\
%       \affaddr{School of Electrical Engineering and Computer Science}\\
%       \affaddr{Oregon State University}\\
%       \email{agroce@gmail.com}
% 2nd. author
%\alignauthor
%Josie Holmes\\
%       \affaddr{Department of Geography}\\
%       \affaddr{Pennsylvania State University}\\
%       \email{webmaster@marysville-ohio.com}
% 3rd. author
%\alignauthor Kevin Kellar\\
%       \affaddr{Crescent Valley High School}\\
%       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
%      \affaddr{Hekla, Iceland}\\
%      \email{larst@affiliation.org}
%}


\begin{abstract}
\input{abstract}
\end{abstract}

\mycomment{

\author{\IEEEauthorblockN{%
Alex Groce,\IEEEauthorrefmark{1}
Josie Holmes\IEEEauthorrefmark{2}
Kevin Kellar\IEEEauthorrefmark{3}
}

\IEEEauthorblockA{\IEEEauthorrefmark{1}%
School of Electrical Engineering and Computer Science\\
Oregon State University\\
\IEEEauthorrefmark{2}
Department of Geography\\
Pennsylvania State University
\IEEEauthorrefmark{3}
Crescent Valley High School
}


}
%\author{\IEEEauthorblockN{Alex Groce, Amin Alipour, Chaoqiang Zhang, Yang Chen, John Regehr}
%\IEEEauthorblockA{School of Electrical Engineering and Computer Science\\
%Oregon State University, Corvallis, OR\\
%Email: agroce@gmail.com, alipourm,zhangch@onid.oregonstate.edu}}
}

\mycomment{
\numberofauthors{1}
\author{
\alignauthor
Arpit Christi, Matthew Lyle Olson, Mohammad Amin Alipour, Alex Groce\\
\affaddr{School of Electrical Engineering and Computer Science}\\
\affaddr{Oregon State University}
\affaddr{Corvallis, OR USA}\\
%\affaddr{Corvallis, OR}\\
%\affaddr{USA}
}
}


\begin{CCSXML}
<ccs2012>
<concept_id>10011007.10011074.10011099.10011102.10011103</concept_id>
<concept_desc>Software and its engineering~Software testing and debugging</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

%%% The following is specific to ISSTA'17 and the paper
%%% 'One Test to Rule Them All'
%%% by Alex Groce, Josie Holmes, and Kevin Kellar.
\setcopyright{acmcopyright} % Adjust this to match your publishing-rights agreement with ACM.
\acmDOI{10.1145/3092703.3092704}
\acmISBN{978-1-4503-5076-1/17/07}
\acmConference[ISSTA'17]{26th International Symposium  on  Software Testing and Analysis }{July 2017}{Santa Barbara, CA, USA} 
\acmYear{2017}
\copyrightyear{2017}
\acmPrice{15.00}

\ccsdesc[500]{Software and its engineering~Software testing and debugging}

\keywords{test case reduction, semantic simplification, fuzzer taming}

\maketitle

\input{intro}

\input{formal}

\input{casestudies}

\input{related}



\input{conclusions}

%\IEEEtriggeratref{21}

%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)

%\def\IEEEbibitemsep{0.6pt plus 0.9pt}

\bibliographystyle{abbrv}
%\bibliography{bibliography}

\begin{thebibliography}{10}

\bibitem{NumPy}
{NumPy}.
\newblock \url{http://www.numpy.org}.

\bibitem{SymPy}
{SymPy}.
\newblock \url{http://www.sympy.org/en/index.html}.

\bibitem{ArcPy}
What is {ArcPy}?
\newblock
  \url{http://resources.arcgis.com/EN/HELP/MAIN/10.1/index.html#//000v000000v7000000}.

\bibitem{AndrewsTR}
J.~Andrews, Y.~R. Zhang, and A.~Groce.
\newblock Comparing automated unit testing strategies.
\newblock Technical Report 736, Department of Computer Science, University of
  Western Ontario, December 2010.

\bibitem{mutant}
J.~H. Andrews, L.~C. Briand, and Y.~Labiche.
\newblock Is mutation an appropriate tool for testing experiments?
\newblock In {\em International Conference on Software Engineering}, pages
  402--411, 2005.

\bibitem{arcuri2014hitchhiker}
A.~Arcuri and L.~Briand.
\newblock A hitchhiker's guide to statistical tests for assessing randomized
  algorithms in software engineering.
\newblock {\em Software Testing, Verification and Reliability}, 24(3):219--250,
  2014.

\bibitem{RandFormal}
A.~Arcuri, M.~Z.~Z. Iqbal, and L.~C. Briand.
\newblock Formal analysis of the effectiveness and predictability of random
  testing.
\newblock In {\em International Symposium on Software Testing and Analysis},
  pages 219--230, 2010.

\bibitem{PLDI13}
Y.~Chen, A.~Groce, C.~Zhang, W.-K. Wong, X.~Fern, E.~Eide, and J.~Regehr.
\newblock Taming compiler fuzzers.
\newblock In {\em ACM SIGPLAN Conference on Programming Language Design and
  Implementation}, pages 197--208, 2013.

\bibitem{SoftBET}
D.~Coppit, J.~Yang, S.~Khurshid, W.~Le, and K.~Sullivan.
\newblock Software assurance by bounded exhaustive testing.
\newblock {\em IEEE Transactions on Software Engineering}, 31(4):328--339, Apr.
  2005.

\bibitem{Guava}
E.~Daka, J.~Campos, J.~Dorn, G.~Fraser, and W.~Weimer.
\newblock Generating readable unit tests for {Guava}.
\newblock In {\em Search-Based Software Engineering - 7th International
  Symposium, {SSBSE} 2015, Bergamo, Italy, September 5-7, 2015, Proceedings},
  pages 235--241, 2015.

\bibitem{Readable}
E.~Daka, J.~Campos, G.~Fraser, J.~Dorn, and W.~Weimer.
\newblock Modeling readability to improve unit tests.
\newblock In {\em Foundations of Software Engineering, {ESEC/FSE}}, pages
  107--118, 2015.

\bibitem{cloc}
A.~Danial.
\newblock {CLOC}: Count lines of code.
\newblock \url{https://github.com/AlDanial/cloc}.

\bibitem{z3}
L.~M. de~Moura and N.~Bj{\o}rner.
\newblock {Z3:} an efficient {SMT} solver.
\newblock In {\em Tools and Algorithms for the Construction and Analysis of
  Systems}, pages 337--340, 2008.

\bibitem{term1}
N.~Dershowitz.
\newblock Termination of rewriting.
\newblock {\em Journal of Symbolic Computing}, 3(1):69--115, 1987.

\bibitem{myxml}
erezbibi.
\newblock \url{https://pypi.python.org/pypi/my_xml/0.1.1}.

\bibitem{Daikon}
M.~Ernst, J.~Cockrell, W.~Griswold, and D.~Notkin.
\newblock Dynamically discovering likely program invariants to support program
  evolution.
\newblock In {\em International Conference on Software Engineering}, pages
  213--224, 1999.

\bibitem{Fow10}
M.~Fowler.
\newblock {\em {Domain-Specific Languages}}.
\newblock Addison-Wesley Professional, 2010.

\bibitem{FA11}
G.~Fraser and A.~Arcuri.
\newblock {EvoSuite}: automatic test suite generation for object-oriented
  software.
\newblock In {\em Proceedings of the 19th ACM SIGSOFT Symposium and the 13th
  European Conference on Foundations of Software Engineering}, ESEC/FSE '11,
  pages 416--419. ACM, 2011.

\bibitem{FraserGen}
G.~Fraser and A.~Zeller.
\newblock Generating parameterized unit tests.
\newblock In {\em Proceedings of the 2011 International Symposium on Software
  Testing and Analysis}, ISSTA '11, pages 364--374, New York, NY, USA, 2011.
  ACM.

\bibitem{Gastin04minimizationof}
P.~Gastin, P.~Moro, and M.~Zeitoun.
\newblock Minimization of counterexamples in {SPIN}.
\newblock In {\em SPIN Workshop on Model Checking of Software}, pages 92--108.
  Springer-Verlag, 2004.

\bibitem{stvrcausereduce}
A.~Groce, M.~A. Alipour, C.~Zhang, Y.~Chen, and J.~Regehr.
\newblock Cause reduction: Delta-debugging, even without bugs.
\newblock {\em Journal of Software Testing, Verification, and Reliability}.
\newblock accepted for publication.

\bibitem{icst2014}
A.~Groce, M.~A. Alipour, C.~Zhang, Y.~Chen, and J.~Regehr.
\newblock Cause reduction for quick testing.
\newblock In {\em IEEE International Conference on Software Testing,
  Verification and Validation}, pages 243--252. IEEE, 2014.

\bibitem{WODACommon}
A.~Groce and M.~Erwig.
\newblock Finding common ground: Choose, assert, and assume.
\newblock In {\em International Workshop on Dynamic Analysis}, pages 12--17,
  2012.

\bibitem{AMAI}
A.~Groce, K.~Havelund, G.~Holzmann, R.~Joshi, and R.-G. Xu.
\newblock Establishing flight software reliability: Testing, model checking,
  constraint-solving, monitoring and learning.
\newblock {\em Annals of Mathematics and Artificial Intelligence},
  70(4):315--349, 2014.

\bibitem{ICSEDiff}
A.~Groce, G.~Holzmann, and R.~Joshi.
\newblock Randomized differential testing as a prelude to formal verification.
\newblock In {\em International Conference on Software Engineering}, pages
  621--631, 2007.

%\vfill\null
\vspace{4in}

\bibitem{WODA08}
A.~Groce and R.~Joshi.
\newblock Random testing and model checking: Building a common framework for
  nondeterministic exploration.
\newblock In {\em Workshop on Dynamic Analysis}, pages 22--28, 2008.

\bibitem{MakeMost}
A.~Groce and D.~Kroening.
\newblock Making the most of {BMC} counterexamples.
\newblock {\em Electron. Notes Theor. Comput. Sci.}, 119(2):67--81, Mar. 2005.

\bibitem{NFM15}
A.~Groce and J.~Pinto.
\newblock A little language for testing.
\newblock In {\em NASA Formal Methods Symposium}, pages 204--218, 2015.

\bibitem{ISSTA15}
A.~Groce, J.~Pinto, P.~Azimi, and P.~Mittal.
\newblock {TSTL}: a language and tool for testing (demo).
\newblock In {\em ACM International Symposium on Software Testing and
  Analysis}, pages 414--417, 2015.

\bibitem{tstl}
A.~Groce, J.~Pinto, P.~Azimi, P.~Mittal, J.~Holmes, and K.~Kellar.
\newblock {TSTL}: the template scripting testing language.
\newblock \url{https://github.com/agroce/tstl}.

\bibitem{SPIN03}
A.~Groce and W.~Visser.
\newblock What went wrong: Explaining counterexamples.
\newblock In {\em SPIN Workshop on Model Checking of Software}, pages 121--135,
  2003.

\bibitem{mutpy}
K.~Halas.
\newblock {MutPy} 0.4.0.
\newblock \url{https://pypi.python.org/pypi/MutPy/0.4.0}.

\bibitem{HamletOnly}
R.~Hamlet.
\newblock When only random testing will do.
\newblock In {\em International Workshop on Random Testing}, pages 1--9, 2006.

\bibitem{slippage}
J.~Holmes, A.~Groce, and A.~Alipour.
\newblock Mitigating (and exploiting) test reduction slippage.
\newblock In {\em Workshop on Automated Software Testing}, 2016.

\bibitem{tstlsttt}
J.~Holmes, A.~Groce, J.~Pinto, P.~Mittal, P.~Azimi, K.~Kellar, and J.~O'Brien.
\newblock {TSTL:} the template scripting testing language.
\newblock {\em International Journal on Software Tools for Technology
  Transfer}, 2017.
\newblock Accepted for publication.

\bibitem{term2}
G.~Huet and D.~C. Oppen.
\newblock Equations and rewrite rules: A survey.
\newblock Technical report, Stanford, CA, USA, 1980.

\bibitem{SortedContainers}
G.~Jenks.
\newblock {SortedContainers} introduction.
\newblock
  \url{http://www.grantjenks.com/docs/sortedcontainers/introduction.html}.

\bibitem{FreeWill}
H.~Jin, K.~Ravi, and F.~Somenzi.
\newblock Fate and free will in error traces.
\newblock In {\em Tools and Algorithms for the Construction and Analysis of
  Systems}, pages 445--458, 2002.

\bibitem{MinUnit}
Y.~Lei and J.~H. Andrews.
\newblock Minimization of randomized unit test cases.
\newblock In {\em International Symposium on Software Reliability Engineering},
  pages 267--276, 2005.

\bibitem{TCminim}
A.~Leitner, M.~Oriol, A.~Zeller, I.~Ciupa, and B.~Meyer.
\newblock Efficient unit test case minimization.
\newblock In {\em International Conference on Automated Software Engineering},
  pages 417--420, 2007.

\bibitem{Lev}
V.~I. Levenshtein.
\newblock Binary codes capable of correcting deletions, insertions, and
  reversals.
\newblock {\em Soviet Physics Doklady}, 10:707--710, 1966.

\bibitem{AutoHelp}
C.~Parnin and A.~Orso.
\newblock Are automated debugging techniques actually helping programmers?
\newblock In {\em International Symposium on Software Testing and Analysis},
  pages 199--209, 2011.

\bibitem{SmartCheck}
L.~Pike.
\newblock {SmartCheck}: automatic and efficient counterexample reduction and
  generalization.
\newblock In {\em {ACM} {SIGPLAN} Symposium on Haskell}, pages 53--64, 2014.

\bibitem{CReduce}
J.~Regehr, Y.~Chen, P.~Cuoq, E.~Eide, C.~Ellison, and X.~Yang.
\newblock Test-case reduction for {C} compiler bugs.
\newblock In {\em ACM SIGPLAN Conference on Programming Language Design and
  Implementation}, pages 335--346, 2012.

\bibitem{lithium}
J.~Ruderman.
\newblock Bug 329066 - {Lithium}, a testcase reduction tool (delta debugger).
\newblock \url{https://bugzilla.mozilla.org/show_bug.cgi?id=329066}, 2006.

\bibitem{jsfunfuzz}
J.~Ruderman.
\newblock Introducing jsfunfuzz, 2007.
\newblock \url{http://www.squarefree.com/2007/08/02/introducing-jsfunfuzz/}.

\bibitem{jsfunfuzz2}
J.~Ruderman.
\newblock Releasing jsfunfuzz and {DOMFuzz}.
\newblock
  \url{https://www.squarefree.com/2015/07/28/releasing-jsfunfuzz-and-domfuzz/},
  2015.

\bibitem{avltree}
user1689822.
\newblock python {AVL} tree insertion.
\newblock
  \url{http://stackoverflow.com/questions/12537986/python-avl-tree-insertion}.

\bibitem{csmith}
X.~Yang, Y.~Chen, E.~Eide, and J.~Regehr.
\newblock Finding and understanding bugs in {C} compilers.
\newblock In {\em ACM SIGPLAN Conference on Programming Language Design and
  Implementation}, pages 283--294, 2011.

\bibitem{DD}
A.~Zeller and R.~Hildebrandt.
\newblock Simplifying and isolating failure-inducing input.
\newblock {\em Software Engineering, IEEE Transactions on}, 28(2):183--200,
  2002.

\bibitem{issta14}
C.~Zhang, A.~Groce, and M.~A. Alipour.
\newblock Using test case reduction and prioritization to improve symbolic
  execution.
\newblock In {\em International Symposium on Software Testing and Analysis},
  pages 160--170, 2014.

\bibitem{SaiSimple}
S.~Zhang.
\newblock Practical semantic test simplification.
\newblock In {\em International Conference on Software Engineering}, pages
  1173--1176, 2013.

\end{thebibliography}


\end{document}
