\subsection{Regression Generation}

One difficulty for ArcPy users is ensuring that their existing scripts
and tools work on new versions of ArcGIS.  Each recent major release
(10.2 and 10.3) after ArcPy's introduction has potentially included some changes
in the behavior of API calls.  Detecting when such changes cause a
script to break is difficult.  A first step would be an automatic way
to find when the return values for calls differ between ArcPy
versions.
Because installing multiple versions of ArcGIS on the same system is
difficult or impossible, our method for finding differences relies on
choosing a reference version (10.3 in our current efforts), and
generating a set of standalone tests that 1) cover a large amount of
ArcPy functionality, including invalid inputs to functions and 2)
record the return values and exceptions raised by calls.  These tests
can be run on any ArcPy version, and will report differences between
the tests and version 10.3.  Performing this kind of differential
testing \cite{Differential} on old or new major releases, or across 64
bit and 32 bit versions, is easy.  In the long run, we also want to
enabled TSTL to produce Python 3.0+ code, for use with ArcGIS Pro,
which uses Python 3.4 instead of 2.7.  This has motivated a branch to
TSTL to support Python 2.7 (unfortunately, Python 3.0 is not fully
backwards compatible with earlier versions, and Python 2.7 is still
the most widely used Python).

We generate regression tests using an approach called \emph{quick
  testing} \cite{icst2014,stvrcausereduce}, which takes a set of tests
produced by random testing, and applies a test case reduction
algorithm \cite{DD} to produce smaller tests that have the same code
coverage as the very large, highly redundant, original set of test
cases.  Automatic quick-testing was added to TSTL's random test
generator to support ArcPy testing.  Combined with standalone test
generation, this allows us to produce test cases that can be run on
any version of ArcPy, and explore a large variety of behavior of the
code.  With ArcPy, coverage alone, unlike previous quick testing
efforts, is insufficient to ensure a useful regression test.  Because
coverage only considers the Python behavior of ArcPy (since we do not
have access to the source for the ArcGIS engine), it may group
behaviors that are not similar together.  We added the ability to
combine coverage preservation with preservation of all ArcPy messages
indicating a successful GIS engine operation, after abstracting away
such details as the runtime of the operation, and so forth.

However, just producing these coverage-and-engine-behavior preserving
standalone tests is not sufficient for good version comparison, since
standalone test cases as produced only check for properties defined in TSTL.  An
additional option was added to the standalone test generator, allowing
it to record the actual return values of all calls, the set of
exceptions thrown, the success/failure messages from the ArcPy engine, and so forth to more precisely record a test's
behavior on an ArcPy version.
